### 2019-09-09 papers/journal/bio.tex
Updated draft with Somya's bio updates-02

\subsubsection{Vesicle fusion} 
The process of vesicle fusion involves two steps: recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}). 
%
Target compartment recognition involves molecular
switches called Rabs and tethering complexes \cite{rink2005rab}. 
%
Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment \cite{muller2018molecular}. 
%
Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two
before fusion \cite{baker2016chaperoning}.

The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
%
There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type. 
%
In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment. 
%
A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs~\cite{yoon2018snare}.

>>>>

\subsubsection{Vesicle fusion} 
The process of vesicle fusion involves two steps: recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}). 
%
Target compartment recognition involves molecular
switches called Rabs and tethering complexes \cite{rink2005rab}. 
%
%Rabs are master regulators; in their active form, 
Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment \cite{muller2018molecular}. 
%
Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two
before fusion \cite{baker2016chaperoning}.

%The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
%
The final step in vesicle transport is the fusion of the vesicle with the target compartment. 
%
It is brought about by SNARE proteins.
%
There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type. 
%
In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment. 
%
A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs~\cite{yoon2018snare}.
